babette: BEAUti 2, BEAST2 and Tracer for R

### 2018-05-07 response_letter/response_letter.md

> Page 6, lines 151-155: For parameters which are changed only using a scale operator, 
> and not a random walk or uniform operator, values less than 0 are never proposed. 
> So effectively the prior probability density for something like birth rate 
> with an unbounded uniform prior is 0 to infinity, 
> and having a non-zero probability on negative values is not a valid reason to use an exponential prior.

We agree and decided to remove the incorrect reasoning altogether and only demonstrate how to use a different
prior distribution.

> Page 7, line 182: Reference to the Bouckaert & Vaughan blog post 
> doesn't seem relevant to this feature of babette. 
> How does babette fix the crown age? 
> Is it by scaling the root node of the tree to that age, 
> and removing all operators that can change the height of the root node? 
> However it is done, adding a brief explanation in the main text would be good.

The reference to the blog post has been removed. 
Indeed, we described how `babette`
fixes a phylogeny crown age, by -indeed- removing 
all operators that can change the height of the root node. 
But, we decided to remove this paragraph altogether, 
because the posteriors produced by BEAST2 with this setting have remarkably different branch length distributions, for unknown reasons. Using a dated node on the crown does give the regular branch length distributions.

@@

> [x] L31. "Figure ??" ?

We completely agree. Fixed.

> [x] L91. Is this the equivalent of running BEAST2 with an empty alignment?

No, that option mentioned was to validate a file to be valid (i.e. not corrupted or
have an incorrect XML structure). We decided to remove 
mentioning file validation in the manuscript,
as it would be only of minor interest to most (it has been moved to a vignette). 
Instead, we mention the option of installing BEAST2 from R.

### 2018-05-07 article.tex
Implemented feedback, thanks @rsetienne

\begin{lstlisting}[language=R, floatplacement=H]
run_beast2(
  input_filename = "beast2.xml",
  output_log_filename = "run.log",
  output_trees_filenames = "posterior.trees",
  output_state_filename = "final.xml.state"
)
\end{lstlisting}
\verb;run_beast2; is a function that only runs BEAST2, 
and does not parse the output files (unlike \verb;bbt_run;). 
In the example above, 
we specify the names of the desired BEAST2 
output files explicitly, and these will be created in the
R working directory, after which thay can be inspected 
with other tools, or used to continue a BEAST2 run.
By default, both \verb;bbt_run; and \verb;run_beast2;
put these files in the default temporary folder (as
created by \verb;temp.dir();) to keep
the working directory clean of intermediate files.

@@

\end{document}
\grid
\grid

>>>>

\begin{lstlisting}[language=R, floatplacement=H]
run_beast2(
  input_filename = "beast2.xml",
  output_log_filename = "run.log",
  output_trees_filenames = "posterior.trees",
  output_state_filename = "final.xml.state"
)
\end{lstlisting}
\verb;run_beast2; is a function that only runs BEAST2, 
and does not parse the output files (unlike \verb;bbt_run;). 
In the example above, 
we specify the names of the desired BEAST2 
output files explicitly, and these will be created in the
R working directory, after which they can be inspected 
with other tools, or used to continue a BEAST2 run.
When the names of these files are not specified, 
both \verb;bbt_run; and \verb;run_beast2;
put these files in the default temporary folder (as
obtained from \verb;temp.dir();) to keep
the working directory clean of intermediate files.

@@

\end{document}
\grid
\grid
\grid
